Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-03-17 paper.tex
Finished 6.2

After done the evaluation, we obtain a set of @VS@ and need to update the @out@ cache.
In the first case of pattern matching, it happens inside of the last continuation of
outer @nd@.
For the second case, we update the @out@ cache before calling the continuation @continue@.

@@

Finally, the @analyze@ function as the entrance of the analysis does a looping iteration
to find the fixed-point on caches starting from an empty cache.
If the @out@ cache of this iteration is equivalent to the @out@ cache from the last iteration,
then we have reached a fixed-point that over-approximates the concrete evaluations,
and thus can be returned.
Otherwise, a next iteration with the new @out@ cache will be activated.
Note that the continuation of the initial call to @aeval@ sets up the values for the
initial configuration in the final cache.

>>>>

After completing the evaluation, we obtain a set of @VS@ objects and must update the @out@ cache.
In the first case of pattern matching, this happens inside the last continuation of the
outer @nd@ call.
For the second case, we update the @out@ cache before calling the @continue@ continuation.

@@

Finally, the @analyze@ function (as the entrance of the analysis) does a looping iteration
to find the fixed-point on caches starting from an empty cache.
If the @out@ cache of this iteration is equivalent to the @out@ cache from the last iteration,
then we have reached a fixed-point that over-approximates the concrete evaluations,
and thus can be returned.
Otherwise, the next iteration with the new @out@ cache will be activated.
Note that the continuation of the initial call to @aeval@ sets up the values for the
initial configuration in the final cache.
